Master's Project Journal

### 2019-03-25 conf_paper/paper.tex
meas1 & 3

\author{\IEEEauthorblockN{C. Dooley, E. Blokhina, B. Mulkeen}
    \IEEEauthorblockA{\textit{School of Electronic Engineering} \\
        \textit{University College Dublin}\\
        Belfield, Dublin 4, Ireland. \\
        conor.dooley@ucdconnect.ie} %TODO
}

@@

\begin{abstract}
    This paper introduces and compares the implementation of a number of FPGA based ADPLL network prototyping architectures. Comparison is then made between the expected performance and role of each method as a development tool.
\end{abstract}

\begin{IEEEkeywords}
    FPGA, ADPLL, Simulation, Prototyping
\end{IEEEkeywords}

>>>>

\author{\IEEEauthorblockN{C. Dooley, E. Blokhina, B. Mulkeen}
    \IEEEauthorblockA{\textit{School of Electrical \& Electronic Engineering, University College Dublin}
}

@@

\begin{abstract}
    This paper introduces and compares the implementation of a number of FPGA based ADPLL network prototyping architectures. Comparison is then made between the expected performance and role of each method as a development tool.
\end{abstract}
